How to compute the fusion product of MV cycles in type A

### 2021-04-08 draft.tex
Updates from Overleaf

\subsection{Groups}
Let $H $ be an algebraic group over $ \CC $.  We will be interested $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.  Note that evaluation at $ t = s$ provides a group homomorphism $ H(\cO_s) \rightarrow H$.  We denote the kernel of this map by $ H_1(\cO_s)$.  We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$ which is often called the first congruence subgroup.
% \acom{Add $G_1$}
%\acom{TODO: Algebraic groups over rings, i.e.\ the meaning of $G(K)$. The affine space of $m\times m$ matrices which we denote $ M_m$. The first congruence subgroup $G_1$ and why we take $\Oinf$ points instead of $\CC[t]$ points as some of the lit does.}

@@

We will also be interested in the affine space $ M_m$ of $m$x$m$ matrices.  Note that for any $ \CC$-algebra $ R $,  $GL_m(R) $ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.  Thus $ t^\lambda \in M_m(\CC[t])$ for all $ \lambda \in P_{++}$ but $ t^\lambda \in GL_m(\CC[t]) $ if and only if $ \lambda = 0 $.

@@

% The trivial lattice is 
% No more: L_0(R) = 
$ R^m \subset K^m $ is called the standard lattice. 
% We will abuse notation and denote $L_0(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
% the set of such lattices 
this set and $\GL_m(K)/\GL_m(R)$, since $ GL_m(R) $ is the stabilizer of the standard lattice. 
\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$. If $e_1,\dots,e_m$ denote the standard basis elements of 
% $L_0(\cO)$ then 
$\cO^m$ then 
$$ 
L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
$$}
% \acom{Maybe abuse notation and warn the reader.}
% \acom{is it clear that $\GL(R^m) \le \GL(K^m)$ is normal?} \jcom{It isn't normal and the quotient is not a group.}

@@

% \jcom{I don't think that we need all this about ``formal disc centered at $s$'' below since we now define this in the rings and discs section.}
% \acom{Ok. We could omit the repetitive ``$X=$'' bits from the display styled alternate descriptions. That way they will fit within the margins.}
% TODO: Just trying it out

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by %\acom{Change $V_0$}
    $$
    % \Gr = 
    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_0^\times $} \right\} \,. 
    $$
    % where $V_0$ is the trivial rank $m$ vector bundle.
    % and $ D_0$ is the formal disc centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \left\{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \right\}\,.
    $$
    We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.  On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap} \acom{Change $V_0$}
    % 
    \item For any $ s \in \CC $, 
    % \acom{should it be $\AA$ instead of $\CC$} 
    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by     $$
    % \Gr_s = 
    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D^\times_s $} \right\}\,.
    $$
    % where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
    % \acom{What about fixing the notation $V_0$ somewhere?}

    We also have a lattice description 
    $$ 
    \Gr_s = \left\{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \right\} \,. 
    $$   
    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
    It is described in modular terms by
    $$
         \Grth = 
         \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
    $$
    % where $D_\infty$ denotes a disc centered at $ \infty$. 
    % \acom{What is the difference between ``a disc'' and ``the formal disc''} \jcom{No difference.}

    We also have a lattice description 
    $$ 
    \Grth = \left\{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \right\}\,.
    $$ % \CC\xT[t^{-1}]^m

    % \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.} \acom{Since $\sf th$ is also the first two letters of ``thin''?} \jcom{That's a good point!  Maybe we could use some kind of bold  Gr (``thick'' letters) or maybe that would be too confusing.} \acom{Ok, it's tentative.}

    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
    It is described in modular terms by \acom{Change $V_0$}
    % {\small
    $$
    % \Grbd = 
    % \begin{aligned}
        \left\{ 
            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} \Vtriv \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$%}
    % 
    The fibre of $\Grbd \to \AA$ over $ s \in \AA $ will be denoted $ \Gr_{0,s} $ and is given by
    % \rcom{why do we have the $s\ne 0$ restriction here} \jcom{it would work when $ s = 0$, but it looks a bit strange there.}
    % 
    $$ 
    % \Gr_{0,s} = 
    G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

    We also have a lattice descriptions 
    % {\small
    \begin{gather*}
    \Grbd = 
    \{ (L,s) :
    % s\in\AA,\,
    % L \subset  \CC(t)^m, s \in \AA 
    \text{$L \subset  \CC(t)^m$ is a $\CC[t]$-lattice trivial at any $ a \ne 0, s$} \} \\
    % , $L$ is 
     \Gr_{0,s} = 
    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
    \end{gather*}%}
    \acom{We do not consistently specify where $s$ is in these definitions}
    % \acom{$s\in\CC$ should be $s\in\AA$?}
    % \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
    % 
    \item The positive parts, 
    \[
        \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO)
    \]
    and
    \[
        {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
    \]
    % $ \Gr^+$ and ${\Grth}^+$, 
    of the affine Grassmannian and the thick affine Grassmannian, respectively. %, are defined as 
    % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
    % $$
    % \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \text{ and } {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. % \CC\xT[t^{-1}] missed a spot  
    % $$
    % 
    In modular terms, $\Gr^+$ (resp. ${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow V_0 $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp. over $ \PP$). \acom{Change $V_0$}

    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the relevant standard lattice. 
    % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.  But I would like to leave the terminology ``trivial at $ a$'' is that ok, or should we write ``standard at $a$''.} 
    % \acom{Oh, I don't know.. is trivialized at $a$? is standardized at $a$? Maybe standard at $a$ is better.. Man I never thought about this interchangeable lingo.} 
    % lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$). % , i.e. $ L \subseteq L_0$.
\end{itemize}
% \acom{enumerate the points for now}
These different versions of the affine Grassmannian are related as follows.

@@

    In group-theoretic terms, this isomorphism is given using the diagonal map
    $$G(\CC[t, t^{-1}, (t-s)^{-1}])/G(\CC[t]) \rightarrow G(\cK)/G(\cO) \times G(\cK_s)/G(\cO_s)
    $$
    This is compatible with the lattice description since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}])/G(\CC[t]) $, we have
    $$
    g \CC[t]^m \otimes_{\CC[t]} \cO = g \cO^m
    $$
    and similarly for $ L(s)$.

@@

    \jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}
\end{enumerate}

@@

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant coweights $\lambda_1, \lambda_2 \in P_{++}$ of sizes $N_1, N_2$  and their sums $ \lambda = \lambda_1 + \lambda_2 $ of size $ N = N_1 + N_2$. 
% Coweights define elements in the various affine Grassmannians which we consider. Warning: We will write only coset representatives for elements of the various Grassmannians; we hope that it is evident which right cosets they represent. 
% the right cosets which they represent are clear from the context.
We consider the following subschemes of the affine Grassmannians.
% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    % \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
    % $$ 
    % L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
    % $$ 
    % \acom{This definition makes sense for any $\lambda\in P$? Also, we don't really need it here---I have moved it up to the lattices section.}
    \item The orbit $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian. \acom{Do we need to justify this.}
    % 
    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}

    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.  
    % By \cite[Proposition 3.1.14]{zhu2016introduction},
    % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
    Over $s=0$ the fibre is shown to be $ \overline{\Gr}^{\lambda_1 + \lambda_2}$ by a theorem of Zhu \cite[Proposition 3.1.14]{zhu2016introduction}.

    Suppose that $ s \ne 0$.  In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.  This open locus is a $ G(\CC[t])$-orbit
    % .  The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ 
    whose lattice description is given in \Cref{le:Grl1l2} below.
    % \acom{Why $G(\CC[t])$. Because we are on the left side!}
\end{itemize}
Now fix two effective coweights $ \mu_1, \mu_2 \in \mathbb N^m$ such that $ \mu_i$ has size $ N_i$ and such that $ \mu_1 + \mu_2 $ is dominant.  Using $ \mu_1, \mu_2$, we define the following subschemes.

\begin{itemize}
    \item The locus $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
    % 
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below. 
    % \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
    % A: Ok thanks!
    % 
    \item The semi-infinite orbit $ S^\mu = N_-(\cK)t^\mu \subset \Gr $.  
    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
    $$
    % S^{\mu_1, \mu_2}_{0,s} = 
    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
    $$
    % TODO: resolve
    % \jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$. 
    % TODO: resolve
    % \acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}

    \jcom{These two statements here require some proof, so perhaps they should be split off as a lemma in ``Rising action''.  I changed $ N$ to $ N_-$.}
    % TODO!

\end{itemize}

\subsection{Matrices}
\acom{Keep fixed $\lambda_i,\mu_i,\lambda, \mu$ arbitrary effective dominant coweights and their sums of size $N$ as in the previous section.} We now consider some subvarieties of the space of $ N\times N$ matrices.

>>>>

\subsection{Groups}
Let $H $ be an algebraic group over $ \CC $.  We will be interested $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.  Note that evaluation at $ t = s$ provides a group homomorphism $ H(\cO_s) \rightarrow H$.  We denote the kernel of this map by $ H_1(\cO_s)$, often called the first congruence subgroup.  We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$.
% \acom{Add $G_1$}
%\acom{TODO: Algebraic groups over rings, i.e.\ the meaning of $G(K)$. The affine space of $m\times m$ matrices which we denote $ M_m$. The first congruence subgroup $G_1$ and why we take $\Oinf$ points instead of $\CC[t]$ points as some of the lit does.}

@@

We will also be interested in the affine space $ M_m$ of $m \times m$ matrices.  Note that for any $ \CC$-algebra $ R $,  $GL_m(R) $ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.  Thus $ t^\lambda \in M_m(\CC[t])$ for all $ \lambda \in P_{++}$ but $ t^\lambda \in GL_m(\CC[t]) $ if and only if $ \lambda = 0 $.

@@

% The trivial lattice is 
% No more: L_0(R) = 
$ R^m \subset K^m $ is called the standard lattice. 
% We will abuse notation and denote $L_0(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
% the set of such lattices 
this set and $\GL_m(K)/\GL_m(R)$, since $ GL_m(R) $ is the stabilizer of the standard lattice. 
%\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$. If $e_1,\dots,e_m$ denote the standard basis elements of 
% $L_0(\cO)$ then 
%$\cO^m$ then 
%$$ 
%L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
%$$}

@@

We now define various version of the affine Grassmannian which will play an important role in this paper.

\begin{definition}
     The \textbf{ordinary affine Grassmannian} $\Gr = G(\cK)/G(\cO)$.
\end{definition}    
    It is described in modular terms by 
    $$
     \Gr = 
    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_0^\times $} \right\} \,. 
    $$

    We also have a lattice description 
    $$ 
    \Gr = \left\{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \right\}\,.
    $$
    We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.  On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap}
    % 
\begin{definition}
 For any $ s \in \CC $, 
    % \acom{should it be $\AA$ instead of $\CC$} 
    the \textbf{ordinary affine Grassmannian} $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. 
\end{definition}    
As above, we have modular and lattice descriptions
\begin{gather*}
    \Gr_s = 
    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D^\times_s $} \right\}\,. \\
    \Gr_s = \left\{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \right\} \,. 
\end{gather*}

\begin{definition}
The \textbf{thick affine Grassmannian} $\Grth = G(\Kinf)/G(\CC[t])$.
\end{definition}
    Again, we have the following modular and lattice descriptions
    \begin{gather*}
         \Grth = 
         \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_\infty $ } \right\}\,. \\
    \Grth = \left\{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \right\}\,.
     % \CC\xT[t^{-1}]^m 
    \end{gather*}
    % \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.} \acom{Since $\sf th$ is also the first two letters of ``thin''?} \jcom{That's a good point!  Maybe we could use some kind of bold  Gr (``thick'' letters) or maybe that would be too confusing.} \acom{Ok, it's tentative.}

    \begin{definition} The (two point) \textbf{Beilinson--Drinfeld Grassmannian} $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
      \end{definition}
    It is described in modular terms by 
    % {\small
    $$
     \Grbd = 
    % \begin{aligned}
        \left\{ 
            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} \Vtriv \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$%}
    % 
    The fibre of $\Grbd \to \AA$ over $ s \in \AA $ will be denoted $ \Gr_{0,s} $ and is given by
    % \rcom{why do we have the $s\ne 0$ restriction here} \jcom{it would work when $ s = 0$, but it looks a bit strange there.}
    % 
    $$ 
    % \Gr_{0,s} = 
    G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

    We also have a lattice descriptions 
    % {\small
    \begin{gather*}
    \Grbd = 
    \{ (L,s) :
    % s\in\AA,\,
    % L \subset  \CC(t)^m, s \in \AA 
    \text{$L \subset  \CC(t)^m$ is a $\CC[t]$-lattice trivial at any $ a \ne 0, s$} \} \\
    % , $L$ is 
     \Gr_{0,s} = 
    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
    \end{gather*}%}
    \acom{We do not consistently specify where $s$ is in these definitions}
    % \acom{$s\in\CC$ should be $s\in\AA$?}
    % \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
    % 
    \begin{definition} The \textbf{positive parts} of $\Gr $ and $\Grth$ are defined by 
    $$
        \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \quad        {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
    $$
    \end{definition}
    In modular terms, $\Gr^+$ (resp. ${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow \Vtriv $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp. over $ \PP$).

    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the relevant standard lattice. 
    % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.  But I would like to leave the terminology ``trivial at $ a$'' is that ok, or should we write ``standard at $a$''.} 
    % \acom{Oh, I don't know.. is trivialized at $a$? is standardized at $a$? Maybe standard at $a$ is better.. Man I never thought about this interchangeable lingo.} 
    % lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$). % , i.e. $ L \subseteq L_0$.

% \acom{enumerate the points for now}
\subsection{Relations between different affine Grassmannians}
These different versions of the affine Grassmannian are related as follows.

@@

    In group-theoretic terms, this isomorphism is given using the diagonal map
    $$G(\CC[t, t^{-1}, (t-s)^{-1}])/G(\CC[t]) \rightarrow G(\cK)/G(\cO) \times G(\cK_s)/G(\cO_s)
    $$
    This is compatible with the lattice description since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}]) $, we have
    $$
    \left( g \CC[t]^m \right) \otimes_{\CC[t]} \cO = g \cO^m
    $$
    and similarly for $ L(s)$.

@@

%    \jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}
\end{enumerate}

@@

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant coweights $\lambda', \lambda'' \in P_{++}$ of sizes $N_1, N_2$  and their sums $ \lambda = \lambda' + \lambda'' $ of size $ N = N_1 + N_2$. 
% Coweights define elements in the various affine Grassmannians which we consider. Warning: We will write only coset representatives for elements of the various Grassmannians; we hope that it is evident which right cosets they represent. 
% the right cosets which they represent are clear from the context.
We consider the following subschemes of the affine Grassmannians.
% 
\begin{definition}
The \textbf{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
\end{definition}
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    Since $ \lambda $ effective, $ t^\lambda \in \Gr^+ $ and so the spherical Schubert variety $\overline{\Gr}^\lambda $ lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
    % 
\begin{definition} The \textbf{fusion of two spherical Schubert varieties} $$ \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA $$
\end{definition}
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda'}\times\overline\Gr^{\lambda''}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}
    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.  
    % By \cite[Proposition 3.1.14]{zhu2016introduction},
    % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
    Over $s=0$ the fibre is $ \overline{\Gr}^{\lambda' + \lambda''}$ (and reduced) by a theorem of Zhu \cite[Proposition 3.1.14]{zhu2016introduction}.

    Suppose that $ s \ne 0$.  In the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''}$ coming from transporting $ \Gr^{\lambda'} \times \Gr^{\lambda''} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.  This open locus is a $ G(\CC[t])$-orbit
    % .  The lattice description of $ \Gr_{0,s}^{\lambda', \lambda''}$ 
    whose lattice description is given in \Cref{le:Grl1l2} below.
    % \acom{Why $G(\CC[t])$. Because we are on the left side!}

As above, since $ \lambda', \lambda'' $ are effective, the map $ \Gr_{0, \AA} \rightarrow \Grth$ restricts to a map $ \Gr^{\lambda', \lambda''}_{0, \AA} \rightarrow \Grth^+$.

Now fix two effective coweights $ \mu', \mu'' \in \mathbb N^m$ such that $ \mu_i$ has size $ N_i$ and such that $ \mu = \mu' + \mu'' $ is dominant.  (We do not require $ \mu', \mu'' $ to be effective.) Using $ \mu, \mu', \mu''$, we define the following subschemes.

\begin{definition}
    The \textbf{Kazhdan-Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
\end{definition}
Since $\mu $ is effective, we see that $ \cW_\mu $ lies inside the positive thick Grassmannian $ \Grth^+$.
    %

    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu $ is given in Lemma \ref{le:Wmu} below. 
    % \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
    % A: Ok thanks!
    % 
\begin{definition} The \textbf{semi-infinite orbit} 
$$ S^\mu = N_-(\cK)t^\mu \subset \Gr $$ 
and the \textbf{fusion of  semi-infinite orbits} 
$$ S^{\mu', \mu''}_{0,\AA} := S^{\mu'} \ast_\AA S^{\mu''} \,.$$  
\end{definition}
If $ s \ne 0 $, then the fibre $S^{\mu', \mu''}_{0,s} $ is given by
    $$
    % S^{\mu', \mu''}_{0,s} = 
    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
    $$
    % TODO: resolve
    % \jcom{Maybe we should introduce the $ L_{\mu', \mu''} $ notation, but I'm not sure it is necessary.}
    On the other hand, if $ s = 0$, then the fibre $S^{\mu', \mu''}_{0,0} $ equals $ S^{\mu' + \mu''}$. 
    % TODO: resolve
    % \acom{changed $\mu$ to $\mu' + \mu''$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda', \lambda''} $}

    \jcom{Still need a reference for why this central fibre is reduced.}

\subsection{Matrices}
 We now consider some subvarieties of the space of $ N\times N$ matrices, again using the $ \lambda, \lambda', \lambda'', \mu, \mu', \mu''$ defined in the previous section.  Recall that $\lambda, \mu $ are partitions of $ N$.

\begin{itemize}
    \item For $ s \in \CC$ 
    % and $\lambda\in P_{++}$
    we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. 
    % \acom{$s\in\AA$?}
    % 
    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
    % 
    \item For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.  Its closure is $ \overline{\OO}^{\lambda', \lambda''}_{0,s} = \bigcup_{\gamma' \le \lambda', \gamma'' \le \lambda''} \OO^{\gamma', \gamma''}_{0,s}$. 
    % \acom{$s\in\AA$?}
    % 
    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
    % 
    \item The family of adjoint orbits $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$ a consequence of Eisenbud and Salten's description/characterization(?) of ``rank varieties'' as proved in \Cref{cor:es}.
